Model LF

### 2022-12-01 max_dp endogen stød.Rmd
Commit

```{r}
plot(((unemp_08 - unemp_bs8)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Change in Unemployment", ylim= c(-300, 3000));
lines(((unemp_04 - unemp_bs4)*1000), col= "black");
lines(((unemp_02 - unemp_bs2)*1000), col= "red");
lines(((unemp_01 - unemp_00)*1000), col= "green");
legend("left", legend=c("All channels", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

@@

>>>>

```{r}
plot(((unemp_08 - unemp_bs8)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Change in Unemployment", ylim= c(-300, 2000));
lines(((unemp_04 - unemp_bs4)*1000), col= "black");
lines(((unemp_01 - unemp_00)*1000), col= "green");
legend("left", legend=c("All channels", "Demand & insurance rate channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black", "green"));
grid()
```

@@

## Case 3 short version

marg_cost_c3_w= (micro_elas_dørs +macro_elas_short )/(1-ur_fag); marg_cost_c3_w
